### 2020-03-04 README.Rmd
readme and pkgdown updates
documention update for check_ordered() and expand_info() along with README and vignette update for hagolloch data and pkgdown::build_site() + devtools::document() only

# timeternR

@@

```{r message = F, warning = F}
library(tidyverse)
library(ggtern)
library(timeternR)
```
```{r}
hagelloch_raw %>%
   dplyr::filter(SEX %in% c("male", "female")) %>%
   ggplot(aes(y = tI, z = tR, color = SEX)) +
       geom_aggregate() + 
       coord_tern() +
       labs(x = "S", y = "I", z = "R",
            color = "Gender")
```

>>>>

# timeternR <img src="man/figures/logo.png" align="right" alt="" width="120" />

@@

```{r message = F, warning = F}
library(tidyverse)
library(ggtern)
library(timeternR)
```
The following example comes from a Measles outbreak in Hagelloch, Germany in 1861. We have data on each child (agent) in the town.
```{r}
hagelloch_raw %>%
  ggplot(aes(y = tI, z = tR)) +
    geom_aggregate() + 
    coord_tern() +
    labs(x = "S", y = "I", z = "R", title = "Town Analysis")
```

Previous work has suggested that the class (`CL`) the student was in effected how the experienced the outbreak. The below figure shows differences in the outbreak relative to this grouping.
```{r}
hagelloch_raw %>% 
  rename(`school grade` = CL) %>%
  group_by(`school grade`) %>%
  summarize(`number of students` = n())

hagelloch_raw %>%
   ggplot(aes(y = tI, z = tR, color = CL)) +
       geom_aggregate() + 
       coord_tern() +
       labs(x = "S", y = "I", z = "R",
            color = "School Grade",
            title = "Town analysis by grade") 
```
